Instructions for developing new pages for the MarineOmics webpage

### 2023-12-16 DRAFT_lncRNA.Rmd
draft lncRNA multiqc

@@

@@

>>>>

# Requirements to run code

Need to following software / programs

```
wget
curl
HiSat
samtools
Stringtie
```
Hardware wise need at least 500 GB disk space, and multiple CPUs otherwise would take extrordinary amoutn of time. Code below was run on machine with 48 CPUs.

@@

Run fastqc

```{r, engine='bash'}

/home/shared/FastQC-0.12.1/fastqc \
-t 40 \
-o ../output/lncRNA \
../data/lncRNA/*fastq.gz

@@

multiqc
```{r, engine='bash'}
cd ../output/lncRNA

eval "$(/opt/anaconda/anaconda3/bin/conda shell.bash hook)"
conda activate
which multiqc
multiqc .
```
